Containers and R---the Rockerverse and beyond

### 2020-01-16 manuscript.Rmd
update RCloud paragraph

**[RCloud](https://github.com/att/rcloud/tree/master/docker)** uses a `rocker/drd` base image for creation of collaborative data analysis and visualisation environments.

>>>>

**RCloud** ([https://rcloud.social](https://rcloud.social)) is a cloud-based platform for data analysis, visualisation and collaboration using R.
It provides a `rocker/drd` base image for easy evaluation of the platform\footnote{\href{https://github.com/att/rcloud/tree/master/docker}{https://github.com/att/rcloud/tree/master/docker}}.
